Fail Faster

### 2025-03-18 paper/paper.tex
little progress towards WU section

\subsubsection{Overhead of Choice Combinators}
The monad functions \texttt{return} and \texttt{bind} aren't the only combinators that incur an
abstraction overhead: all of them do! \jwc{I'm so bad at starting new sections...} ``Choice'' combinators like \texttt{weighted\_union}, however
are particularly costly, because they unavoidably allocate a lot.

@@

% \jwc{This builds the cdf of the distribution, samples from 0 to the total, and binary searches through the array to find the bucket.}
% \jwc{Allocating this array is unnecessary: we can simply compute the total weight, sample \texttt{x} between 0 and the total, and then walk the list accumulating the sum, until the accumulator exceeds \texttt{x}. Since in practice the list of possible options is quite small (usually at most 10 in practice), the linear time scan is going to be much faster.}
% \jwc{(The point of this para will just be to emphasize that it's almost always better to be allocation-aware, instead of algorithmically clever.)}

>>>>

\subsubsection{Overhead of Choice Combinators}
After the \texttt{return}, \texttt{bind}, and base-type generation combinators
(such as \texttt{gen\_int}), the most frequently used combinators are ``choice''
combinators like \texttt{weighted\_union} which randomly select between
sub-generators.

Like \texttt{return} and \texttt{bind}, these combinators incur a performance penalty
at run time.

@@
